\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-31 docs/parco13/paper.tex
Comment
Add sphere table

\begin{figure}
  \begin{center}
  \begin{minipage}{.4\columnwidth}
    \begin{tabular}{cc}
      timing table for sphere & 123, \\
    \end{tabular}
  \end{minipage}
  \hspace{.05\columnwidth}
  \includegraphics[width=.4\columnwidth]{../figs_misc/sphere_partition5}
\end{center}
\caption{Partition of the spherical Example 2 between five MPI processors, indicated
  by the color scale, at simulated time $T = 1$.  The partition shows the mesh equator,
  while the refinement is invariant under the number of processors and the partition
and follows the front, which is not aligned with the equator.}
\label{fig:spherical}
\end{figure}
To demonstrate a multiblock connectivity, we include results for Example 2 in
\Fig{spherical}, together with a strong scaling table that shows that the spherical
example scales as well.

@@

We would like to thank the Texas Advanced Computing Center (TACC) for access to
the Stampede supercomputer under allocation TG-DPP130002.
The authors acknowledge valuable discussion with Randy LeVeque, Marsha
Berger, and Hans-Petter Langtangen.  We also acknowledge David
Ketcheson and the KAUST sponsored HPC$^3$ numerics workshop at which
the initial phases of this project were first discussed.  The second
author would like to also acknowledge the Isaac Newton Institute
(Cambridge, UK), where much of the preliminary development work for
\forestclaw was done. The leaf/patch paradigm was independently
presented by B.\ as part of a talk at the SCI Institute, Salt Lake City, Utah,
USA in July 2011.

>>>>

\begin{figure}
  \begin{center}
    \hspace{.1\columnwidth}
    \begin{minipage}[c]{.4\columnwidth}
      \includegraphics[width=.99\columnwidth]{../figs_misc/sphere_partition5}
    \end{minipage}
    \hspace{.05\columnwidth}
    \begin{minipage}[c]{.4\columnwidth}
    \begin{tabular}{r|r}
       $P$ & time int./step \\
      \hline
       16 & 1.115 \\
       32 & 0.557 \\
       64 & 0.297 \\
      256 & 0.092 \\
    \end{tabular}
  \end{minipage}
\end{center}
\caption{Left: Partition of the spherical Example 2 between five MPI processors, indicated
  by the color scale, at simulated time $T = 1$.  The partition shows the mesh equator,
  while the refinement is invariant under the number of processors and the partition
  and follows the front, which is not aligned with the equator.  Right: Strong scaling
  for a uniform run at level 8.}
\label{fig:spherical}
\end{figure}
To demonstrate a multiblock connectivity, we include results for Example 2 in
\Fig{spherical}, together with a strong scaling table that shows that the spherical
example scales as well.

@@

We would like to thank the Texas Advanced Computing Center (TACC) for access to
the Stampede supercomputer under allocation TG-DPP130002 granted by the NSF.
The authors acknowledge valuable discussion with Randy LeVeque, Marsha
Berger, and Hans-Petter Langtangen.  We also acknowledge David
Ketcheson and the KAUST sponsored HPC$^3$ numerics workshop at which
the initial phases of this project were first discussed.  The second
author would like to also acknowledge the Isaac Newton Institute
(Cambridge, UK), where much of the preliminary development work for
\forestclaw was done. The leaf/patch paradigm was independently
presented by B.\ as part of a talk at the SCI Institute, Salt Lake City, Utah,
USA in July 2011.
